---
title: "mini-assignment-4-2_NOTES"
author: "Margaret Taub"
date: "2022-11-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Improve the code: Question 1

1. Using the code in the two functions above, write a function called `means_ci()` that takes the arguments listed below and returns either a 95% confidence interval for a single mean or a 95% confidence interval for the difference in means depending on those arguments.  I've given default values for these arguments as well.

* `x` (no default value)
* `y` (default value is `NULL` which corresponds to `one.mean` option for the `type` argument)
* `type` (default value is `one.mean`, other value is `two.means`)
* `...` (to be able to pass the `na.rm` option through to the mean/sd functions as needed)

Consider including a a way to check whether the vectors of `x` and `y` are numeric and thus such a confidence interval is appropriate.

```{r}
means_ci <- function(x, y = NULL, type = one.mean, ...) {
    if (is.numeric(y)) {
    xbar <- mean(x, ...)
  ybar <- mean(y, ...)
  
  estimate <- xbar - ybar
  
  n_x <- sum(!is.na(x))
  n_y <- sum(!is.na(y))
  s_x <- sd(x, ...)
  s_y <- sd(y, ...)
  
  se <- sqrt(s_x^2/n_x + s_y^2/n_y)
             
  estimate + c(2, -2) * se
    }

   else{ xbar <- mean(x, ...)
  n <- sum(!is.na(x))
  se <- sd(x, ...) / sqrt(n)
  xbar + c(2, -2) * se
} } 

```


```{r}
means_ci <- function(x, y = NULL, type = NULL, ...) {
  
  if (!is.numeric(x)) {
    stop ("`x` and `y` must be a numeric vector")
  }
  if (identical(type, NULL)) {
    xbar <- mean(x, ...)
    n <- sum(!is.na(x))
    se <- sd(x, ...) / sqrt(n)
    xbar + c(2, -2) * se
 } else if (identical(type, "two.means")) {
      xbar <- mean(x, ...)
      ybar <- mean(y, ...)
  
      estimate <- xbar - ybar
  
      n_x <- sum(!is.na(x))
      n_y <- sum(!is.na(y))
      s_x <- sd(x, ...)
      s_y <- sd(y, ...)
  
      se <- sqrt(s_x^2/n_x + s_y^2/n_y)
             
      estimate + c(2, -2) * se
  }
}

```

```{r}

means_ci <- function(x, y = NULL, type = "one.mean", ...){
  if (!is.numeric(x)) {
    stop("`x` must be a numeric vector")
  }
  
if(type == "one.mean"){
  xbar <- mean(x, ...)
  n <- sum(!is.na(x))
  se <- sd(x, ...) / sqrt(n)
  xbar + c(2, -2) * se
}
  else if(type == "two.means"){
    xbar <- mean(x, ...)
  ybar <- mean(y, ...)
  
  estimate <- xbar - ybar
  
  n_x <- sum(!is.na(x))
  n_y <- sum(!is.na(y))
  s_x <- sd(x, ...)
  s_y <- sd(y, ...)
  
  se <- sqrt(s_x^2/n_x + s_y^2/n_y)
             
  estimate + c(2, -2) * se
    }
}

```

## Improve the code: Question 2


```{r}
means_ci <- function(x, y = NULL, type = "one.mean", conf.level = 0.95, ...) {
  
  xbar <- mean(x, ...)
  
  if (type == "one.mean") {
    n <- sum(!is.na(x))
    se <- sd(x, ...) / sqrt(n)
    
    if (conf.level == 0.90) {
      return (xbar + c(1.65, -1.65) * se)
    } else if (conf.level == 0.99) {
        return (xbar + c(2.6, -2.6) * se)
    } else {
      return (xbar + c(2, -2) * se)
    }
    
  } else {
    ybar <- mean(y, ...)
  
    estimate <- xbar - ybar
  
    n_x <- sum(!is.na(x))
    n_y <- sum(!is.na(y))
    s_x <- sd(x, ...)
    s_y <- sd(y, ...)
  
    se <- sqrt(s_x^2/n_x + s_y^2/n_y)
    
    if (conf.level == 0.90) {
      return (estimate + c(1.65, -1.65) * se)
    } else if (conf.level == 0.99) {
        return (estimate + c(2.6, -2.6) * se)
    } else {
        return(estimate + c(2, -2) * se)
    }
             
  }
}


```

```{r}
means_ci <- function(x, y = NULL, type = NULL, conf.level = 0.95, ...) {
  
  if (!is.numeric(x)) {
    stop ("`x` and `y` must be a numeric vector")
  }
    xbar <- mean(x, ...)
    n <- sum(!is.na(x))
    se <- sd(x, ...) / sqrt(n)
  if (identical(type, NULL) & identical(conf.level, 0.95)) {
    xbar + c(2, -2) * se
  } else if (identical(type, NULL) & identical(conf.level, 0.99)) {
   xbar + c(2.6, -2.6) * se
  } else if (identical(type, NULL) & identical(conf.level, 0.90)) {
   xbar + c(1.65, -1.65) * se
 } else if (identical(type, "two.means")) {
      xbar <- mean(x, ...)
      ybar <- mean(y, ...)
  
      estimate <- xbar - ybar
  
      n_x <- sum(!is.na(x))
      n_y <- sum(!is.na(y))
      s_x <- sd(x, ...)
      s_y <- sd(y, ...)
  
      se <- sqrt(s_x^2/n_x + s_y^2/n_y)
             
      estimate + c(2, -2) * se
 }
}


```

```{r}
means_ci2 <- function(x, y = NULL, type = "one.mean", ...) {

   if (is.numeric(x)) {
     
      xbar <- mean(x, ...)
  n <- sum(!is.na(x))
  se <- sd(x, ...) / sqrt(n)
  xbar + c(2, -2) * se }
  
  else{
    
    "`x` must be a numeric vector"
  }
  
   if (identical(conf, 0.95)) {
    xbar + c(2, -2) * se
     
  } else if (identical(conf, 0.99)) {
    xbar + c(2.6, -2.6) * se
    
  } else if  (identical(conf, 0.90)) {
     xbar + c(1.65, -1.65) * se
  
  } else {
    "Confidence level not found; please use 0.95, 0.90, or 0.99"
  }

  if(type == "one.mean") {
    
     xbar <- mean(x, ...)
  n <- sum(!is.na(x))
  se <- sd(x, ...) / sqrt(n)
  xbar + c(2, -2) * se 
  
  } else if (type == "two.means") {

    
  xbar <- mean(x, ...)
  ybar <- mean(y, ...)
  
   estimate <- xbar - ybar
  
  n_x <- sum(!is.na(x))
  n_y <- sum(!is.na(y))
  s_x <- sd(x, ...)
  s_y <- sd(y, ...)
  
  se <- sqrt(s_x^2/n_x + s_y^2/n_y)
             
  estimate + c(2, -2) * se
    
  }
  
}


```

